si: code and prose exploring Spatial Interaction models

### 2022-04-25 README.qmd
Update README to mention mobility
Thanks @luukvdmeer


Former-commit-id: 99a0772bb3957ae3d2ff737f87d95d46f862ba05

- The [`spflow` R package](https://github.com/LukeCe/spflow) on CRAN
- The [`spint` Python package](https://spint.readthedocs.io/en/latest/)
- The [`gravity`](https://cran.r-project.org/package=gravity) R package

>>>>

- The [`spflow` R package](https://github.com/LukeCe/spflow)
- The [`spint` Python package](https://spint.readthedocs.io/en/latest/)
- The [`gravity`](https://cran.r-project.org/package=gravity) R package
- The [`mobility`](https://covid-19-mobility-data-network.github.io/mobility/index.html) R package
